The FAIRification of research in real-world evidence: A practical introduction to reproducible analytic workflows using Git and R

### 2023-06-30 manuscript/manuscript.qmd
corrected word count
added missing citation for the here package
corrected gitlab to github url

[**Word count:**]{.underline} 3,028 words

@@

```{bash}
mkdir ~/rwe_study
cd ~/rwe_study
git clone  https://gitlab.com/USERNAME/rwe_study.gitlab.io.git
```

@@

The use of absolute paths will make it impossible for any collaborator to run the code without having to manually adapt every single path throughout a repository which is tedious and time consuming. A better solution to this is the use of relative paths. A popular R package to implement this is the `here` package which enables file referencing in project-oriented workflows. The main function "`here"` creates paths relative to the top-level of the project directory (in our example the `rwe_study` directory). Applied to our example project, the following command would automatically reference the correct path and could be used without modification by any user re-running this script.

>>>>

[**Word count:**]{.underline} 3,033 words

@@

```{bash}
mkdir ~/rwe_study
cd ~/rwe_study
git clone https://github.com/USER/rwe_study.git
```

@@

The use of absolute paths will make it impossible for any collaborator to run the code without having to manually adapt every single path throughout a repository which is tedious and time consuming. A better solution to this is the use of relative paths. A popular R package to implement this is the `here` package[@here] which enables file referencing in project-oriented workflows. The main function "`here"` creates paths relative to the top-level of the project directory (in our example the `rwe_study` directory). Applied to our example project, the following command would automatically reference the correct path and could be used without modification by any user re-running this script.
